---
title: "Week 1 Exercises"
author: "Marven Noa"
date: "July 7, 2024"
output: pdf_document
---

Please complete all exercises below WITHOUT using any libraries/packages.

# Exercise 1
Assign 10 to the variable x. Assign 5 to the variable y. Assign 20 to the variable z.

```{r ex1}
x <- 10 
y <- 5
z <- 20

```


# Exercise 2
Show that x is less than z but greater than y.

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex2}
result <- (x > y & x < z)

result

```

# Exercise 3
Show that x and y do not equal z. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**

```{r ex3}
result2 <- (x != z) && (y != z)
result2

```


# Exercise 4
Show that the formula `x + 2y = z`. 

**Note: your output must be a SINGLE boolean**

```{r ex4}
result3 <- (x +2*y) == z
result3

```

# Exercise 5
I have created a vector (test_vector) of integers for you. Determine if any of x, y, or z are in the vector. 

**Note: your output must be a SINGLE boolean, do not output a boolean for each expression.**


```{r ex5}
test_vector <- c(1,5,11:22)
result4 <- any(c(x, y, z) %in% test_vector)
result4

```

# Exercise 6
Show which value is contained in the test vector. To do this you will need to create an element-wise logical vector using operators. `x == vector`. Once you have done that you will need to use slicing to return all indices that have matches.
**Note: your output should be two integers**

```{r ex6}

#logical vector
x_in_vector <- test_vector == x
y_in_vector <- test_vector == y
z_in_vector <- test_vector == z

# logical vectors combined
matches <- x_in_vector | y_in_vector | z_in_vector

# Indices that match
matching_indices <- which(matches)
matching_indices



```

